A numerical experiment investigating the influence of drag in trajectory patterns of floating macroalgae

### 2021-03-17 thesis_chapter_3.Rmd
appendix updated

# Appendix

@@

@@

Min_Kfloat_H100_W00_July$type <- "Min_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_July$velocity <- with(Min_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_July$type <- "Min_Kfloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_July$velocity <- with(Min_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_July$type <- "Min_Kfloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_July$velocity <- with(Min_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_July$type <- "Min_Kfloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_July$velocity <- with(Min_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_July$type <- "Mean_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_July$velocity <- with(Mean_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_July$type <- "Mean_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_July$velocity <- with(Mean_KFloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_July$type <- "Mean_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_July$velocity <- with(Mean_KFloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_July$type <- "Mean_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_July$velocity <- with(Mean_KFloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_July$type <- "Max_KFloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_July$velocity <- with(Max_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_July$type <- "Max_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_July$velocity <- with(Max_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_July$type <- "Max_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_July$velocity <- with(Max_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_July$type <- "Max_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_July$velocity <- with(Max_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H100_W00_Oct$type <- "Min_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_Oct$velocity <- with(Min_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_Oct$type <- "Min_Kfloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_Oct$velocity <- with(Min_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_Oct$type <- "Min_Kfloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_Oct$velocity <- with(Min_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_Oct$type <- "Min_Kfloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_Oct$velocity <- with(Min_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_Oct$type <- "Mean_Kfloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_Oct$velocity <- with(Mean_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_Oct$type <- "Mean_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_Oct$velocity <- with(Mean_KFloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_Oct$type <- "Mean_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_Oct$velocity <- with(Mean_KFloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_Oct$type <- "Mean_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_Oct$velocity <- with(Mean_KFloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_Oct$type <- "Max_KFloat_H100_W00" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_Oct$velocity <- with(Max_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_Oct$type <- "Max_KFloat_H095_W05" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_Oct$velocity <- with(Max_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_Oct$type <- "Max_KFloat_H090_W10" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_Oct$velocity <- with(Max_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_Oct$type <- "Max_KFloat_H085_W15" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_Oct$velocity <- with(Max_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

```{r, message=FALSE, echo=FALSE, warning=FALSE}

@@

ggarrange(waterdrag_plot_July, wwdrag_plot_July, waterdrag_plot_Oct, wwdrag_plot_Oct, labels = "AUTO")

@@

>>>>

@@

## April

p_RK4_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/RK4_PFloat_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00")) 
p_RK4_mean_April <- p_RK4_April %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

p_RK4_July$type <- "RK4_April" # add extra column 'type' to dataframe and assigned 'RK4' label

Min_Kfloat_H100_W00_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Min_KFloat_H100_W00_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H100_W00_mean_April <- Min_Kfloat_H100_W00_April %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H100_W00_April$type <- "Min_Kfloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_April$velocity <- with(Min_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

Min_Kfloat_H095_W05_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Min_KFloat_H095_W05_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H095_W05_mean_April <- Min_Kfloat_H095_W05_April %>% # calculate mean trajectory
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H095_W05_April$type <- "Min_Kfloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_April$velocity <- with(Min_Kfloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))

Min_Kfloat_H090_W10_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Min_KFloat_H090_W10_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H090_W10_mean_April <- Min_Kfloat_H090_W10_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H090_W10_April$type <- "Min_Kfloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_April$velocity <- with(Min_Kfloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))

Min_Kfloat_H085_W15_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Min_KFloat_H085_W15_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Min_Kfloat_H085_W15_mean_April <- Min_Kfloat_H085_W15_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Min_Kfloat_H085_W15_April$type <- "Min_Kfloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_April$velocity <- with(Min_Kfloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))

Mean_Kfloat_H100_W00_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Mean_KFloat_H100_W00_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_Kfloat_H100_W00_mean_April <- Mean_Kfloat_H100_W00_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_Kfloat_H100_W00_April$type <- "Mean_Kfloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_April$velocity <- with(Mean_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))

Mean_KFloat_H095_W05_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Mean_KFloat_H095_W05_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_KFloat_H095_W05_mean_April <- Mean_KFloat_H095_W05_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_H095_W05_April$type <- "Mean_KFloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_April$velocity <- with(Mean_KFloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))

Mean_KFloat_H090_W10_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Mean_KFloat_H090_W10_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_KFloat_H090_W10_mean_April <- Mean_KFloat_H090_W10_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_H090_W10_April$type <- "Mean_KFloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_April$velocity <- with(Mean_KFloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))

Mean_KFloat_H085_W15_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Mean_KFloat_H085_W15_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Mean_KFloat_H085_W15_mean_April <- Mean_KFloat_H085_W15_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Mean_KFloat_H085_W15_April$type <- "Mean_KFloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_April$velocity <- with(Mean_KFloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))

Max_Kfloat_H100_W00_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Max_KFloat_H100_W00_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H100_W00_mean_April <- Max_Kfloat_H100_W00_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H100_W00_April$type <- "Max_KFloat_H100_W00_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_April$velocity <- with(Max_Kfloat_H100_W00_April, sqrt(kelpvelU^2 + kelpvelV^2))

Max_Kfloat_H095_W05_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Max_KFloat_H095_W05_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H095_W05_mean_April <- Max_Kfloat_H095_W05_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H095_W05_April$type <- "Max_KFloat_H095_W05_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_April$velocity <- with(Max_Kfloat_H095_W05_April, sqrt(kelpvelU^2 + kelpvelV^2))

Max_Kfloat_H090_W10_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Max_KFloat_H090_W10_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H090_W10_mean_April <- Max_Kfloat_H090_W10_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H090_W10_April$type <- "Max_KFloat_H090_W10_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_April$velocity <- with(Max_Kfloat_H090_W10_April, sqrt(kelpvelU^2 + kelpvelV^2))

Max_Kfloat_H085_W15_April <- tidync("OceanParcels/trajectory_data/chapter3_additional/Max_KFloat_H085_W15_April.nc") %>%
  hyper_tibble() %>%
  dplyr::select(trajectory, lon, lat, time, distance, kelpvelU, kelpvelV) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2018-01-01 00:00:00"))
Max_Kfloat_H085_W15_mean_April <- Max_Kfloat_H085_W15_April %>% #calculate mean trajectory 
  group_by(t) %>% 
  summarise(across(lon:lat, mean, na.rm= TRUE))

Max_Kfloat_H085_W15_April$type <- "Max_KFloat_H085_W15_April" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_April$velocity <- with(Max_Kfloat_H085_W15_April, sqrt(kelpvelU^2 + kelpvelV^2))

total_data_April <- rbind(Min_Kfloat_H100_W00_April, Min_Kfloat_H095_W05_April, Min_Kfloat_H090_W10_April, Min_Kfloat_H085_W15_April, Mean_Kfloat_H100_W00_April, Mean_KFloat_H095_W05_April, Mean_KFloat_H090_W10_April, Mean_KFloat_H085_W15_April, Max_Kfloat_H100_W00_April, Max_Kfloat_H095_W05_April, Max_Kfloat_H090_W10_April, Max_Kfloat_H085_W15_April)

@@

Min_Kfloat_H100_W00_July$type <- "Min_Kfloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_July$velocity <- with(Min_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_July$type <- "Min_Kfloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_July$velocity <- with(Min_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_July$type <- "Min_Kfloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_July$velocity <- with(Min_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_July$type <- "Min_Kfloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_July$velocity <- with(Min_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_July$type <- "Mean_Kfloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_July$velocity <- with(Mean_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_July$type <- "Mean_KFloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_July$velocity <- with(Mean_KFloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_July$type <- "Mean_KFloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_July$velocity <- with(Mean_KFloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_July$type <- "Mean_KFloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_July$velocity <- with(Mean_KFloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_July$type <- "Max_KFloat_H100_W00_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_July$velocity <- with(Max_Kfloat_H100_W00_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_July$type <- "Max_KFloat_H095_W05_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_July$velocity <- with(Max_Kfloat_H095_W05_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_July$type <- "Max_KFloat_H090_W10_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_July$velocity <- with(Max_Kfloat_H090_W10_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_July$type <- "Max_KFloat_H085_W15_July" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_July$velocity <- with(Max_Kfloat_H085_W15_July, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H100_W00_Oct$type <- "Min_Kfloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H100_W00_Oct$velocity <- with(Min_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H095_W05_Oct$type <- "Min_Kfloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H095_W05_Oct$velocity <- with(Min_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H090_W10_Oct$type <- "Min_Kfloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H090_W10_Oct$velocity <- with(Min_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Min_Kfloat_H085_W15_Oct$type <- "Min_Kfloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Min_Kfloat_H085_W15_Oct$velocity <- with(Min_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_Kfloat_H100_W00_Oct$type <- "Mean_Kfloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_Kfloat_H100_W00_Oct$velocity <- with(Mean_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H095_W05_Oct$type <- "Mean_KFloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H095_W05_Oct$velocity <- with(Mean_KFloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H090_W10_Oct$type <- "Mean_KFloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H090_W10_Oct$velocity <- with(Mean_KFloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Mean_KFloat_H085_W15_Oct$type <- "Mean_KFloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Mean_KFloat_H085_W15_Oct$velocity <- with(Mean_KFloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H100_W00_Oct$type <- "Max_KFloat_H100_W00_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H100_W00_Oct$velocity <- with(Max_Kfloat_H100_W00_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H095_W05_Oct$type <- "Max_KFloat_H095_W05_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H095_W05_Oct$velocity <- with(Max_Kfloat_H095_W05_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H090_W10_Oct$type <- "Max_KFloat_H090_W10_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H090_W10_Oct$velocity <- with(Max_Kfloat_H090_W10_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

Max_Kfloat_H085_W15_Oct$type <- "Max_KFloat_H085_W15_Oct" # add extra column 'type' to dataframe and assigned 'kelp' label
Max_Kfloat_H085_W15_Oct$velocity <- with(Max_Kfloat_H085_W15_Oct, sqrt(kelpvelU^2 + kelpvelV^2))

@@

```{r, message=FALSE, echo=FALSE, warning=FALSE}
waterdrag_plot_April <- ggplot()+
  #geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_April, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_April, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Mean_Kfloat_H100_W00_mean_April, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H100_W00_mean_April, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

wwdrag_plot_April <- ggplot()+
  #geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID), size = 1.0, colour = "black", fill = NA) +
  geom_path(data = p_RK4_mean_April, aes(x = lon, y = lat), color = 'black')+
  geom_path(data = Min_Kfloat_H095_W05_mean_April, aes(x = lon, y = lat), color = 'grey')+
  geom_path(data = Min_Kfloat_H090_W10_mean_April, aes(x = lon, y = lat), color = 'green')+
  geom_path(data = Min_Kfloat_H085_W15_mean_April, aes(x = lon, y = lat), color = 'pink')+
  geom_path(data = Mean_KFloat_H095_W05_mean_April, aes(x = lon, y = lat), color = 'yellow')+
  geom_path(data = Mean_KFloat_H090_W10_mean_April, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Mean_KFloat_H085_W15_mean_April, aes(x = lon, y = lat), color = 'red')+
  geom_path(data = Max_Kfloat_H095_W05_mean_April, aes(x = lon, y = lat), color = 'blue')+
  geom_path(data = Max_Kfloat_H090_W10_mean_April, aes(x = lon, y = lat), color = 'orange')+
  geom_path(data = Max_Kfloat_H085_W15_mean_April, aes(x = lon, y = lat), color = 'red')+
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme_bw()

@@

ggarrange(waterdrag_plot_April, wwdrag_plot_April, waterdrag_plot_July, wwdrag_plot_July, waterdrag_plot_Oct, wwdrag_plot_Oct, labels = "AUTO", ncol = 2, nrow = 3)

```
In the April simulations, both passive and kelp particles followed the general north-westward flow of the region with clear entrainment of kelp particles in sub-mesoscale features. Kelp particles follow the north

@@

## April

heatmap_RK4_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4_April, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  scale_fill_continuous(type = "gradient", limits = c(1, 13000)) +
  geom_path(data = p_RK4_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("30") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H100_W00_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00_April, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "gradient",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H100_W00_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H100W100") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H095_W05_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05_April, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "gradient",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H095_W05_mean_April, aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  #ggtitle("H095W05") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H090_W10_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10_April, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "gradient",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H090_W10_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H090W10") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H085_W15_April <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15_April, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "gradient",        limits = c(1, 13000)) +
  geom_path(data = Min_Kfloat_H085_W15_mean_April,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H085W15") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
